# Version 1 

```{r setup, echo = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

I think it would be helpful to have a chunk with all the libraries to load at the top. 
Oh I see now, pacman is a library to help load in packages! Never heard of it, super interesting!
```{r}
install.packages("pacman")
library(pacman)
install.packages("afex")
library(afex)
```

```{r settings}
rm(list=ls())
pacman::p_load(tidyverse, here, fs, glue, afex, emmeans, knitr, psych, scales, plotly, RColorBrewer)
options("scipen" = 4)
```

```{r helperfunc}
# merge different files
multmerge = function(filenames){
  datalist = lapply(filenames, function(x){read_delim(file=x, delim = "\t")})
  Reduce(function(x,y) {merge(x,y, all.x = TRUE, all.y = TRUE)}, datalist)
}
```

```{r dir-setting}
# Directories
proj_dir <- path(here())
color_dir <- path(proj_dir, "data","data_beh_color_lure")
asso_dir <- path(proj_dir, "data","data_beh_asso_lure")
exclu_color_dir <- path(proj_dir, "data","exclude_color")
exclu_asso_dir <- path(proj_dir, "data","exclude_asso")
```


```{r data}
# get the single file name
allfiles_color = dir(color_dir, pattern='.csv', recursive=TRUE)
# add the data fold name
allfiles_color = paste(color_dir, allfiles_color, sep = "/")
# all color test data
dat_col <- multmerge(allfiles_color)

# get the single file name
allfiles_asso = dir(asso_dir, pattern='.csv', recursive=TRUE)
# add the data fold name
allfiles_asso = paste(asso_dir, allfiles_asso, sep = "/")
# all asso test data
dat_asso <- multmerge(allfiles_asso)


# get the single file name
exc_asso = dir(exclu_asso_dir, pattern='.csv', recursive=TRUE)
# add the data fold name
exc_asso = paste(exclu_asso_dir, exc_asso, sep = "/")
# all asso test data
dat_exc_asso <- multmerge(exc_asso)

# get the single file name
exc_color = dir(exclu_color_dir, pattern='.csv', recursive=TRUE)
# add the data fold name
exc_color = paste(exclu_color_dir, exc_color, sep = "/")

# all color test data
dat_exc_col <- multmerge(exc_color)

dat_asso$Group <- rep('Successful',nrow(dat_asso))
dat_col$Group <- rep('Successful',nrow(dat_col))
dat_exc_asso$Group <- rep('Struggling',nrow(dat_exc_asso))
dat_exc_col$Group <- rep('Struggling',nrow(dat_exc_col))
dat_exc_asso$SubjID <- dat_exc_asso$SubjID*10
dat_exc_col$SubjID <- dat_exc_col$SubjID*10
dat_asso <- rbind(dat_asso,dat_exc_asso)
dat_col <- rbind(dat_col,dat_exc_col)
```


```{r absolute-error}
# Color memory test data


dat_col$Abs_Err <- abs(dat_col$RotateAng-dat_col$colchoice)
i = 0
# dealing with the 355 - 12 error
for (i in seq_along(dat_col$Abs_Err)){
  if (abs(360-dat_col$Abs_Err[i]) < dat_col$Abs_Err[i]){
    dat_col$Abs_Err_corr[i] <- abs(360-dat_col$Abs_Err[i])
  }
  else{dat_col$Abs_Err_corr[i] <- dat_col$Abs_Err[i] }
}
```

```{r Color-Bias}
# negative value for driven away
# positive value for driven closer
# dealing with the overflow issue
for (i in seq_along(dat_col$Abs_Err)){
  if (dat_col$PairNo[i] %% 2 == 1){
    if (abs(360-dat_col$Abs_Err[i]) < dat_col$Abs_Err[i]){
      if (dat_col$colchoice[i] < dat_col$RotateAng[i]){
        dat_col$Col_Bia[i] <- dat_col$Abs_Err_corr[i]
      }
      else{
        dat_col$Col_Bia[i] <- -dat_col$Abs_Err_corr[i]
      }
    }
    else{
      if (dat_col$colchoice[i] < dat_col$RotateAng[i]){
        dat_col$Col_Bia[i] <- -dat_col$Abs_Err_corr[i]
      }
      else{
        dat_col$Col_Bia[i] <- dat_col$Abs_Err_corr[i]
      }
    }
  }
  else{
    if (abs(360-dat_col$Abs_Err[i]) < dat_col$Abs_Err[i]){
      if (dat_col$colchoice[i] < dat_col$RotateAng[i]){
        dat_col$Col_Bia[i] <- -dat_col$Abs_Err_corr[i]
      }
      else{
        dat_col$Col_Bia[i] <- dat_col$Abs_Err_corr[i]
      }
    }
    else{
      if (dat_col$colchoice[i] < dat_col$RotateAng[i]){
        dat_col$Col_Bia[i] <- dat_col$Abs_Err_corr[i]
      }
      else{
        dat_col$Col_Bia[i] <- -dat_col$Abs_Err_corr[i]
      }
    }
  }
}

```

```{r guesses-away-from-competitor}
for (i in seq_along(dat_col$Abs_Err)){
  if (dat_col$Col_Bia[i] < 0){dat_col$away[i] <- 1}
  else{dat_col$away[i] <- 0}
}
```



```{r asso-data}
# Associative memory test data

dat_asso <- na.omit(dat_asso)
dat_asso$SubjID <- as.factor(dat_asso$SubjID)
dat_asso$RunNo <- as.factor(dat_asso$RunNo)
# specify hit/lure/foil
for (i in seq_along(dat_asso$facechoice)){
  if (dat_asso$facechoice[i] == 1){dat_asso$hit[i] = 1}
  else{dat_asso$hit[i] = 0}
  
  if (dat_asso$facechoice[i] == 2){dat_asso$lure[i] = 1}
  else{dat_asso$lure[i] = 0}
  
  if (dat_asso$facechoice[i] == 3 |dat_asso$facechoice[i] == 4){dat_asso$foil[i] = 1}
  else{dat_asso$foil[i] = 0}
}
```

```{r}
dat_col_subj <- dat_col %>% 
  mutate(SubjID = as.factor(SubjID)) %>% 
  group_by(SubjID,Group) %>% 
  summarise(Abs_Err_mean = mean(Abs_Err_corr),
            Col_bia_mean = mean(Col_Bia),
            away_mean = mean(away))
```


```{r }
dat_asso_subj <- dat_asso %>% 
  mutate(SubjID = as.factor(SubjID)) %>% 
  group_by(Group,SubjID, RunNo) %>% 
  summarise(hit_mean = mean(hit),
            lure_mean = mean(lure),
            foil_mean = mean(foil),
            RT_mean =mean(RT)) %>% 
  ungroup()

dat_asso_hit <- dat_asso_subj %>% 
  dplyr::select(Group,SubjID, RunNo, hit_mean) %>% 
  spread(key = RunNo, hit_mean)




color_cor <- dat_asso_hit %>% 
  dplyr::select(-(3:12)) %>% 
  mutate(last_four_round_mean = (`11`+`12`+`13`+`14`)/4) %>% 
  mutate(SubjID = as.factor(SubjID)) %>% 
  left_join(dat_col_subj) %>% 
  mutate(Group = as.factor(Group))

for (i in seq_along(color_cor$Col_bia_mean)){
             color_cor$Col_bia_mean[i] = -color_cor$Col_bia_mean[i]
             }

# m <- aov_ez(data = color_cor, id = "SubjID", dv = "Col_bia_mean", between = "Group")
# t <- afex_plot(m, x = "Group", error_ci = FALSE, return = "data", error = "between")
# f <- magrittr::extract2(t, 1)%>%
#   rename(Group = x, Col_bia_mean = y)
```



## Figure 1
```{r fig.cap='Color bias results by groups',out.width='80%', fig.asp=.75, fig.align='center'}
plot1 <- ggplot(color_cor,aes(x = Group, y = Col_bia_mean, fill = Group)) +
  geom_bar(stat ="summary", fun.y = "mean", width = 0.3) +
  geom_jitter(width = 0.05) + 
  geom_hline(aes(yintercept=0), colour="#990000", linetype="dashed") +
  ylab("Color Bias (degree)") +
  xlab("Group")  + 
  scale_x_discrete(limits=c("Successful","Struggling")) +
  theme_minimal() + 
  ylim(-20, 10) +
  scale_fill_brewer(palette = "Set1")

plot1 + theme(axis.title.x = element_text(size=14),
           axis.text.x= element_text(size=12),
           axis.title.y = element_text(size=14),
           axis.text.y= element_text(size=12))
# this is just a suggestion, but I think it's easier to read the labels with a slightly larger font. 
```
For figure 1 I really like the use of the individual data points over the bars; it helps view the variation! You could also lower the alpha in the bars so that points on the blue bars stick out a little more!

I think it would be helpful to make the font for all the labels a little bigger. 

It seems that message is pretty clear that those in the struggling group have a greater negative color bias. 

## Figure 2
```{r fig.cap='Correlation between the accuracy of the last run of the associative memory test and the color bias',out.width='80%', fig.asp=.75, fig.align='center'}
color_cor_exc <- color_cor
cor(color_cor_exc$`14`,color_cor$Col_bia_mean)
cor.test(color_cor_exc$`14`,color_cor$Col_bia_mean)
model <- lm(Col_bia_mean ~ `14`, color_cor_exc)
xmin <- min(color_cor_exc$`14`)
xmax <- max(color_cor_exc$`14`)
predicted <- data.frame( `14` = seq(xmin,xmax,length.out = 100))
colnames(predicted)[1] <- '14'
predicted$Col_bia_mean <- predict(model,predicted)

ggplot(color_cor_exc,aes(y=Col_bia_mean, x=`14`)) +
  geom_point(aes(colour = Group))+
  ylab("Color bias") +
  xlab("Accuracy of the last run of the associative memory test")+
  scale_x_continuous(labels=percent) + ylim(-20,10) +
  geom_smooth(method = "lm", se = F, color = "grey30") +
  theme_minimal() +
  scale_color_brewer(palette = "Set1")
```
As in the last figure, the message is pretty clear which I appreciate! I like theme minimal because it directs me right to the data. I think you could increase font size of the labels and take out the zeros after the decimal places on the x axis! Another fun thing you could do is highlight the outlines using gghlighlight.

## Figure 3
```{r fig.cap='Accuracy across 14 runs of the associative memory test of the successful group', out.width='80%', fig.asp=.75, fig.align='center'}
dat_dyn <- dat_asso_subj %>% 
  filter(Group == "Successful") 
d <- highlight_key(dat_dyn, ~SubjID)

p <- ggplot(d, aes(RunNo, hit_mean, group = SubjID)) +
  geom_line() +
  ylim(0,1) +
  ylab("Accuracy") +
  xlab("#Run")+ 
  theme(legend.position="none")+
  scale_y_continuous(labels=percent)+
  theme_minimal() 
gg <- ggplotly(p, tooltip = "SubjID") 
highlight(gg, on = "plotly_hover", dynamic = TRUE)
```

This one is so cool! I really like being able to interact with the plot and even change the brush color. I like that lines are gray and not black it helps the chosen line pop out. I also like that you choose not to have a legend because it's not really necessary. For the x axis label I think you could remove the # sign because the information is available in the caption. My only other comment is to remove the zeros after the decimal points on the y axis. 
